From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-28 Pi+/paper/ufin.tex
More on UFin

>>>>

At level 0, all we know is that if $X : \UFin[3]$, then X is merely equal to $\Fin[3]$, that is
$\Trunc[-1]{X \id \Fin[3]}$, and we don't have access to the bijection. At level 1, if we know that both $X$ and $Y$ are
\emph{equal} in $\UFin[3]$, then we can extract an equivalence between them, that is, $(X \id Y) \to (X \eqv Y)$.
$\UFin[3]$ being a univalent subuniverse asserts that there are as many elements (upto higher homotopy) in $X \id Y$ as
there are $X \eqv Y$.
